### 2024-07-08 basic-statistics.qmd
20240707 - interval/ratio
20240707 - Cohen cite

Effect size thresholds [@McGrath2006] for small, medium, and large effect sizes are in @tbl-effectSizeThresholds.

@@

A Statistical Decision Tree For Choosing an Appropriate Statistical Procedure. Adapted from: <https://commons.wikimedia.org/wiki/File:InferentialStatisticalDecisionMakingTrees.pdf>. The original source is: Corston, R. & Colman, A. M. (2000). *A crash course in SPSS for Windows*. Wiley-Blackwell. Changes were made to the original, including the addition of several statistical tests.
:::

>>>>

Effect size thresholds [@Cohen1988; @McGrath2006] for small, medium, and large effect sizes are in @tbl-effectSizeThresholds.

@@

A Statistical Decision Tree For Choosing an Appropriate Statistical Procedure. Adapted from: <https://commons.wikimedia.org/wiki/File:InferentialStatisticalDecisionMakingTrees.pdf>. The original source is: Corston, R. & Colman, A. M. (2000). *A crash course in SPSS for Windows*. Wiley-Blackwell. Changes were made to the original, including the addition of several statistical tests. *Note*: "Interval" as a level of measurement includes data with an "[interval](#sec-interval)" or higher level of measurement; thus, it also includes data with a "[ratio](#sec-ratio)" level of measurement.
:::
